%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

\vspace{1mm}

\fontspec[Path = fonts/lato/]{Lato-Lig}\fontsize{20pt}{15cm}\selectfont Michael Jeffrey Wu \vspace{3mm}\\
\color{headings}\fontspec[Path = fonts/lato/]{Lato-Lig}\fontsize{11pt}{14pt}\selectfont 
\href{mailto:michaeljeffreywu@gmail.com}{{\FA \faEnvelope} \,\, {michaeljeffreywu@gmail.com}} \\
\href{https://github.com/mistermjtek}{{\FA \faGithubSign} \,\,\, {mistermjtek}} \\
\href{https://www.linkedin.com/in/michaeljeffreywu}{{\FA \faLinkedinSign} \,\,\, {in/michaeljeffreywu}} \\
\rule{6cm}{0.4pt} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\subsection{BS in Physiology \&}
\subsection{Neuroscience}
\descript{University of California, San Diego}
\location{Expected December 2016 | La Jolla, CA}
\sectionsep

\subsection{Minor in Computer Science}	
\descript{University of California, San Diego}
\location{June 2015 | La Jolla, CA}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\bubble{Javascript} \hspace{2mm} \bubble{AngularJS} \hspace{2mm} \bubble{ReactJS} \\ 
\vspace{4mm}
\bubble{HTML \& CSS} \hspace{2mm} \bubble{NodeJS} \hspace{2.5mm} \bubble{MongoDB} \\
\vspace{4mm}
\bubble{AJAX} \hspace{2mm} \bubble{ D3} \hspace{2mm} \bubble{Java} \hspace{2.5mm} \bubble{Python} \hspace{2mm} \bubble{Git} \\
\sectionsep
\sectionsepextra

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TOOLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Tools}
\bubble{Sublime Text} \hspace{2mm} \bubble{Terminal} \hspace{2.5mm}  \bubble{Slack} \\ 
\vspace{4mm}
\bubble{Chome Dev Tools} \hspace{1mm} \bubble{Sketch} \hspace{2.5mm} \bubble{Illustrator}
\sectionsep
\sectionsepextra

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Algorithms \\
Data Structures \\
Web Design \\
Discrete Mathematics \\
Human-Computer Interaction\\
Data Visualization \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\bubble{UI Design} \hspace{2.5mm} \bubble{User Research} \hspace{2mm} \bubble{Startups} \\
\vspace{4mm}
\bubble{Data Visualization} \hspace{1.5mm} \bubble{Open Source}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\color{headings}\vline
\hfill
\begin{minipage}[t]{0.58\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
I am a front end developer focused on building beautiful and optimized applications. My passion is learning and using the most recent application frameworks to create scalable products for small companies looking to grow or large companies looking for better user experiences. I believe great user interfaces that understand human needs are the driving force of today's successful businesses.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Adventure Bucket List}
\descript{| Front-end Developer}
\location{2014 -- 2015 | Sunnyvale, CA}
\descriptsep
Developed the MVP front-end web application for clients to begin using to process transactions.
Built out the travel operator dashboard for clients to manage their customers, metrics and activities.
Used AngularJS, REST, NodeJS, MongoDB, Jade, LiveScript, Sass, Material Design to create a scalable product. Integrated the application widget to several travel operators around the world. Started off as an intern and promoted to a full-time position. Led a small team of developers \& designers and tracked their workflow via Github \& Trello.
\sectionsep
\sectionsepextra

\runsubsection{SynergySuite}
\descript{| Mobile Developer}
\location{2014 -- 2015 | Mountain View, CA}
\descriptsep
Built an enterprise mobile app from the ground up deployed to all devices using Cordova/Phonegap, Ionic, Angular.js. Created interactive graphs using D3.js for clients to view analytics. Joined the team as an intern and promoted to a year-round part-time position. Discussed with customers about feature requests and bug fixes. Released private beta mobile app onto Google Play Store and App Store.
\sectionsep
\sectionsepextra

\runsubsection{Blanket Warriors}
\descript{| Contributor}
\location{2015 | San Francisco, CA}
\descriptsep
Developing a website that helps new programmers find resources and view projects built on modern javascript frameworks. Projects are open sourced and can be viewed on Github @Blanket-Warriors\sectionsep
\sectionsepextra

\runsubsection{Statim Health}
\descript{| Web Developer}
\location{June 2014 –- August 2014 | Sunnyvale, CA}
\descriptsep 
Created a website demo designed to pitch to venture capitalists in the Silicon Valley. Redesigned and developed the pending landing page.
\sectionsep
\sectionsepextra


\runsubsection{Monte Jade Science \& Tech}
\descript{| Web Developer}
\location{2013 -- 2014 | San Jose, CA}
\descriptsep 
Redesigned and integrated new functionalities into montejade.org. Created multiple prototypes and mockups; new styling guide, logo and brand. Integrated Twitter Bootstrap, Mailchimp, Javascript/jQuery, etc. Deployed event page to help fundraise for organization.
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
