%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Spencer}{Boucher}{
\href{mailto:spencer.g.boucher@gmail.com}{spencer.g.boucher@gmail.com} \\
\urlstyle{same}\url{spencerboucher.com} \\
650-946-7257
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{MS in Analytics}
\descript{University of San Francisco}
\location{June 2014 | San Francisco, CA \\ GPA: 3.8}
\sectionsep

\subsection{BA in Cognitive Sciences}
\descript{Rice University}
\location{May 2011 | Houston, TX}
Neuroscience concentration \\
\location{GPA: 3.5}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIAL
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Social} 
\href{https://github.com/justmytwospence}{{\FA \faGithubSign} \,\, \custombold{justmytwospence}} \\
\href{https://www.linkedin.com/in/spencerboucher}{{\FA \faLinkedinSign} \,\, \custombold{in/spencerboucher}} \\
\href{https://twitter.com/justmytwospence}{{\FA \faTwitter} \,\, \custombold{@justmytwospence}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
Python \textbullet{} R \textbullet{} SQL \textbullet{} SAS \textbullet{} \\
Javascript \textbullet{} HTML \textbullet{} CSS \textbullet{} \LaTeX\ \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
Text Mining \\
Machine Learning \\
Multivariate Statistics \\
Distributed Computing \\
Data Visualization \\
Distributed Databases \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
	2008 & Eagle Scout & BSA \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
data \textbullet{} design \textbullet{} stories \textbullet{} \\
visualization \textbullet{} cartography 


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{AutoGrid}
\descript{| intern}
\location{2013 | Redwood City, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Used Pandas and R to munge large volumes of smart-meter data. Built time- series and cross-sectional models to identify outliers and make forecasts. Pro- duced several interactive tools and maps for exploring the raw data.
\sectionsep

\runsubsection{Stanford CIBSR}
\descript{| research assistant}
\location{2011 -- 2013 | Stanford, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Conducted MRI studies to investigate biomarkers of pediatric bipolar disorder in at-risk patients, ages 8–20. Operated MRI scanners and analyze structural and functional neuroimaging data using Matlab and R. Performed exploratory and hypothesis-driven analysis of large multi-modal data. Presented findings at the 2012 American Academy of Adolescent and Child Psychiatry Conference.
\sectionsep

\runsubsection{Examkrackers}
\descript{| course instructor}
\location{Jan 2013 –- May 2013 | Palo Alto, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Taught MCAT-level physics, chemistry, biology, organic chemistry, and verbal reasoning to a class of ~12 students.
\sectionsep

\runsubsection{Baylor CPU}
\descript{| project intern}
\location{2009 -- 2011 | Houston, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Conducted fMRI studies with patient populations suffering from PTSD or drug dependency. Analyzed functional neuroimaging data using MATLAB. Investi- gated the relationship between affective phenotypes, including resilience, and neural response to emotional stimuli, and presented research findings at the 2010 Society for Neuroscience convention.
\sectionsep

\runsubsection{Rice EMS}
\descript{| emergency medical technician}
\location{2010 -- 2011 | Houston, TX}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Responded to traumatic and medical emergencies on the Rice University cam- pus with appropriate patient care / transport. Served weekly 12 hour shifts and completed a minimum of 24 hours per semester volunteering for outside EMS services in the greater Houston area
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
